\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-08 paper/main.tex
add raw version of brain structures to cluster tables

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech. Clusters sorted by voxel size.}
\label{tab:cope1}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
\label{tab:cope3}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
\label{tab:cope5}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}

@@

% results
% von Interpretation klar(er) getrennt halten
figure \ref{fig:results}
words > no-speech \ref{tab:cope1}
proper nouns > coordinate conjunctions and proper nouns \ref{tab:cope3}
nouns > coordinate conjunctions \ref{tab:cope5}
The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
left lateralization (bigger cluster left in BA XY => Broca)
The contrasts proper nouns > coordinate conjunctions and nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.

% discussion
% careful what you pretend, check & cite (again)
% \citep{binder2009semantic, dewitt2012phoneme}.
Discussion: alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research

>>>>

% hier die Lateralisation in den Broca Arealen BA44 und BA45 klarer machen
\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech. Clusters sorted by voxel size. The first brain structure given contains the voxel with the maximum Z-Value.}
\label{tab:cope1}
\begin{tabular}{rrrrrrrrrp{6cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & l Heschl's G.; lateral superior Occipital C., Angular G., posterior Supramarginal G., middle Temporal G. posterior to anterior; part of Planum Temporale, anterior superior Temporal G. \\
14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & r. Superior Temporal G.; Angular G., Supramarginal G., middle Temporal G. posterior to anterior, Heschl's G. , inferior Frontal Gyrus pars opercularis (BA44); parts of Planum Temporale \& pars triangularis (BA45) \\
1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & frontal Orbital C.; Precentral G. (Broca's area BA44), pars triangularis \& Inferior Frontal G.; part of pars opercularis (Broca's area BA44); NO Precentral Gyrus \\
217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & l. Thalamus \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size. The first brain structure given contains the voxel with the maximum Z-Value.}
\label{tab:cope3}
\begin{tabular}{rrrrrrrrrp{6cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & l. Planum Temporale; Angular G., Supramarginal G., Heschl's G., Superior Temporal G., Planum Polare, Temporal Pole \\
5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & r Parietal Operculum, Planum Temporale; Heschl's G., superior Temporal G., Planum Polare, Temporal Pole; part of Angular G. \\
479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & l. posterior Cingulate G. \\
420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & l. Precuneus \\
407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & r. posterior Cingulate C. \\
294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & r. Preceus \\
121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & r. Occipital Pole \\
117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & r. Heschl's G. \\
115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & l. superior lateral Occipital C.\\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size. The first brain structure given contains the voxel with the maximum Z-Value.}
\label{tab:cope5}
\begin{tabular}{rrrrrrrrrp{6cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & l. anterior superior Temporal G.; posterior Supramarginal G., Parietal Operculum, Planum Temporale, anterior superior Temporal G., Planum Polare; part of Heschl's Gyrus \\
1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & r. Planum Temporale, Superior Temporal Gyrus; part of Heschl's G. \& Planum Polare \\
166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & r. posterior Cingulate G. \\
149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & r. Precuneus \\
\bottomrule
\end{tabular}
\end{table*}

@@

% results
% von Interpretation klar(er) getrennt halten
figure \ref{fig:results}
words > no-speech \ref{tab:cope1}
proper nouns > coordinate conjunctions and proper nouns \ref{tab:cope3}
nouns > coordinate conjunctions \ref{tab:cope5}
Results: The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
left lateralization (bigger cluster left in BA XY => Broca)
The contrasts proper nouns > coordinate conjunctions and nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.

% discussion
% careful what you pretend, check & cite (again)
% \citep{binder2009semantic, dewitt2012phoneme}.
Discussion: alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research
All contrasts show bilateral clusters in speech-related regions (e.g. ) but all bigger in voxel count on the left side => Clear involvement of the right hemisphere but bias to the left (see \citep{hamilton2018revolution}
